A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2022-01-12 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}[t]
    \centering
    \subfloat[\centering Projector calibration image (2D pattern position detections overlain).]{{\includegraphics[width=5.85cm]{images/detections_.png}}}
    \quad
    \subfloat[\centering Recovered 3D positions corresponding to projector calibration image for use in projector calibration (red, in scene plane).]{{\includegraphics[height=4.75cm]{images/2d3d.pdf}}}
    \caption{Obtaining the 3D positions of the 2D-3D correspondences for use in projector calibration. (a) For each target location, a projector calibration image is acquired from the viewpoint of the `downwards-facing' camera, containing a projected asymmetric circle pattern at the target location and a chessboard pattern placed on the floor nearby. Circle pattern center points and chessboard corners detected automatically (overlain for illustration). (b) Given a projector calibration image, the scene plane is recovered in the coordinate frame of the `downwards-facing' camera (black with up vector red) via spatial resection with respect to 2D-3D correspondences obtained using the chessboard pattern (blue); the 3D positions of the 2D-3D correspondences to be used in calibrating the projector (red, in scene plane) are obtained by intersection with the scene plane of the back-projections (rays, likewise gray) of the 2D center points of the circle pattern detected in the image plane of the camera.} %The corresponding 2D positions are detected in the image of the asymmetric circles pattern image projected by the projector (not shown). The `downwards-facing' camera is shown relative to the scene plane in terms of its camera frustum (black, with up vector in red).
    \label{fig:2d}
\end{figure}

@@

\paragraph{2D-3D correspondences for camera calibration} We recover 2D-3D correspondences in support of calibrating the `downwards-facing' camera by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern, and is such a pattern that we use as well. The 3D corner points of the chessboard are obtained \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners ($8~\times{}~7$ squares), with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---since our projector calibration relies on the camera calibration---the units of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting be off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, respectively, and the resulting list of correspondences is used to recover the camera calibration matrix~$\mathtt{K}_\text{cam}$.

@@

\begin{figure}[t]
    \centering
    \subfloat[\centering Oblique view (annotated).]{{\includegraphics[height=5.25cm]{images/3_cam_.pdf}}}
    \qquad
    \subfloat[\centering View directly downwards to scene~plane.]{{\includegraphics[height=5.25cm]{images/3_above3_cam.png}}}
    \caption{Obtaining the virtual camera. Our physical `downwards-facing' camera---placed to face downwards towards the scene plane, and in terms of whose rotation relative to the normal vector of the scene plane we wish to orient our augmentations---is almost certain to not face downwards towards the scene plane precisely. Accordingly, we rotate the recovered `downwards-facing' camera (frustum in black) about its center of projection such that its optical axis be made parallel with the scene plane's normal, with respect to the minimum arc-length rotation relating the two.} %It is then, for each respective target location, the $X$- and $Y$-axes of the resulting \textit{virtual} camera (gray) that we subsequently use to orient the virtual projector (cf.\ Figure~\ref{fig:virtualproj}) in terms of which the augmentation is to appear to be projected, which is itself placed to face downwards towards the scene plane precisely. The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera. This rotated camera is our virtual camera, and it is the orientation of the virtual camera that we subsequently use to orient our virtual projector.
    \label{fig:virtualcam}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfloat[\centering Projector calibration image (2D position detections of chessboard pattern and asymmetric circle pattern overlain).]{{\includegraphics[width=5.85cm]{images/detections_.png}}}
    \quad
    \subfloat[\centering Recovery of corresponding 3D positions of asymmetric circle pattern for use in projector calibration (red, in scene plane).]{{\includegraphics[height=4.75cm]{images/2d3d.pdf}}}
    \caption{Obtaining the 3D positions of the 2D-3D correspondences for use in projector calibration. (a) For each target location, a projector calibration image is acquired from the viewpoint of the `downwards-facing' camera, containing a projected asymmetric circle pattern at the target location and a chessboard pattern placed on the floor nearby. Circle pattern center points and chessboard corners detected automatically (overlain for illustration). (b) Given a projector calibration image, the scene plane is recovered in the coordinate frame of the `downwards-facing' camera (frustum in black with up vector red) via spatial resection with respect to 2D-3D correspondences obtained using the chessboard pattern (blue), with 3D positions known \textit{a priori}. With the scene plane available, the 3D positions of the projected asymmetric circles pattern to be used in calibrating the projector (red, in scene plane) are obtained by intersection with the scene plane of the back-projections (gray rays) of the detected 2D center points of the circle pattern (red, in image plane of camera).} %The corresponding 2D positions are detected in the image of the asymmetric circles pattern image projected by the projector (not shown). The `downwards-facing' camera is shown relative to the scene plane in terms of its camera frustum (black, with up vector in red).
    \label{fig:2d}
\end{figure}

@@

\paragraph{2D-3D correspondences for camera calibration} We recover 2D-3D correspondences in support of calibrating the `downwards-facing' camera by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern, and is such a pattern that we use as well. The 3D corner points of the chessboard are known \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners ($8~\times{}~7$ squares), with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---since our projector calibration relies on the camera calibration---the units of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting be off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, respectively, and the resulting list of correspondences is used to recover the camera calibration matrix~$\mathtt{K}_\text{cam}$.

@@

\begin{figure}[t]
    \centering
    \subfloat[\centering Oblique view (annotated).]{{\includegraphics[height=5.25cm]{images/3_cam.pdf}}}
    \qquad
    \subfloat[\centering View directly downwards to scene~plane.]{{\includegraphics[height=5.25cm]{images/3_above3_cam.png}}}
    \caption{Obtaining the virtual camera. Our physical `downwards-facing' camera---placed to face downwards towards the scene plane, and in terms of whose rotation relative to the normal vector of the scene plane we wish to orient our augmentations---is almost certain to not face downwards towards the scene plane precisely. Accordingly, we rotate the recovered `downwards-facing' camera (frustum in black) about its center of projection such that its optical axis be made parallel with the scene plane's normal, with respect to the minimum arc-length rotation relating the two.} %It is then, for each respective target location, the $X$- and $Y$-axes of the resulting \textit{virtual} camera (gray) that we subsequently use to orient the virtual projector (cf.\ Figure~\ref{fig:virtualproj}) in terms of which the augmentation is to appear to be projected, which is itself placed to face downwards towards the scene plane precisely. The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera. This rotated camera is our virtual camera, and it is the orientation of the virtual camera that we subsequently use to orient our virtual projector.
    \label{fig:virtualcam}
\end{figure}
